StreamReduce: A Data Stream Processor with MapReduce Parallelism

### 2012-05-16 paper/paper.tex
Final edits

For example, if the distribution of words in the test corpus is close to uniform, the top-k
words are bunched together and any perturbations in the transformation,
such as discarding an
article that contains instances of the real top-k words, may affect the fidelity of the
reported top-k. However, if there is sufficient separation among words in the input,
transformations that discard words may still report an accurate top-k.

@@

The distribution of words in the Wikipeida data set is
shown in Figure~\ref{fig:wordDist}. The distribution is long-tailed, which may indicate
that this data set can withstand the perturbations introduced by StreamReduce.

@@

This significant spacing in the top~100 words makes it likely that the input will produce an
accurate result when StreamReduce transforms it by discarding data.

@@

Anything less than perfect computation of a datum leaves out words with a frequency of one.
Figure~\ref{fig:recall} shows how recall improves as the work level increases. Task killing has
the same effect on recall as using low fidelity computation routines, so recall decreases as
the task kill rate does. Task killing dominates the impact of work level on recall as
demonstrated by the two lines converging in Figure~\ref{fig:recall}.

>>>>

For example, if the distribution of words in the test corpus is close to uniform, the top-k
words are bunched together and any perturbations in the transformation,
such as discarding an
article that contains instances of the real top-k words, may affect the fidelity of the
reported top-k. However, if there is sufficient separation among words in the input,
transformations that discard words should still report an accurate top-k.

@@

The distribution of words in the Wikipeida data set is
shown in Figure~\ref{fig:wordDist}. The distribution is long-tailed, which indicates
that the result from this data set should be robust in the face of
the perturbations introduced by StreamReduce.
%this data set can withstand the perturbations introduced by StreamReduce.

@@

This significant spacing in the top~100 words makes it likely that
StreamReduce will produce an accurate result when transforming this particular input.

@@

Anything less than perfect computation of a datum may leave out words with a frequency of one.
Figure~\ref{fig:recall} shows how recall improves as the work level increases. Task killing has
the same effect on recall as using low fidelity computation routines, so recall decreases as
the task kill rate does. Task killing dominates the impact of work level on recall as
demonstrated by the two lines converging in Figure~\ref{fig:recall}.
